---
title: "linear model from Web"
author: "Madeleine Alseryani"
date: "Spring 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

In this scatterplot we can see that as you move to the right, the SIMS increases. So the more to the right we go, the higher it increases. Therefore, this scatterplot has a positive correlation.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation value from this data and scatterplot is 0.6860073

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
We know that the smaller the value for the residual standard error, the better the model will be. And the larger the adjusted R-squared value, the better the model will be as well. According to the inferential results, we can see that the adjusted R-squared value is 0.467 and the residual standard error is 1.226. 


```{r}
newdata<-data_frame(ARM=88, GRIP=94)
```



#### Predict at target point


```{r}
predict(model.1,newdata,interval="prediction")
```

Based off of predicting the target point, we get a predicted value of 0.7 and we also get a confidence interval from -1.7 to 3.13. This allows us to predict model 1.

#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point() + geom_lm()
```

This scatterplot shows the best fit for this scatterplot. We can see that the line is pointing in a positive direction because it has a positive correlation.

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

This scatterplot shows the same kind of pattern that the first scatterplot shows. As you move towards the right, the SIMS increases. So it looks like its going uphill and right hence, it has a positive correlation. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data= data)
```

The correlation value from this scatterplot is 0.6398458

### Inferential  (Build model.2)
  
  ```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

Based on the inferential results, the residual standard error is 1.295 and the adjusted R-squared is 0.4053. We can see that model 1 has a smaller value for the residual standard error and a larger adjusted R-squared value. Whereas, in this model we have a larger residual standard error value and a smaller adjusted R-squared value.

#### predict model.2 at target point

```{r}
predict(model.2,newdata,interval="prediction")
```


The prediction for model 2 at the target point is -0.536 and the confidence interval is from -3.107 to 2.03.

#### now add the model fit to our plot for model.2
  
```{r}
basicNG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
```{r}
basicNG + geom_point() + geom_lm()
```

This is the model fit for the scatter plot in model 2. It looks somewhat similar to model 1.

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
  The correlation value for model 3 which is a combination of SIMS, ARM, and GRIP is 0.7326545.
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

This data gives us the equation in order to predict SIMS. The residual standard error is 1.144 and the adjusted R-squared is 0.5358. Therefore, model 3 is better because the residual standard error values for the other two models are bigger and the adjusted R-squared values for the other two models are lower (we want this value to be larger). Hence, model 3 is a better fit than model 1 and model 2.

#### predict model.3 at target point
  
```{r}
predict(model.3,newdata,interval="prediction")
```

The prediction at target point for model 3 is 0.149 and the confidence interval is -2.1323 to 2.431. 

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```

In this data set, we can see that model 1 and model 3 are nested. We can see that when all of the errors were added up they came out to be 217.88 and when they were removed they came out to be 188.43. The errors were reduced by about 30.The p-value is significant because it is a very low value so the results are significant. 

### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```

In this data set, model 2 and model 3 are nested. We can see that the errors in this case were dropped by 50 and the p-value is even much lower.

## Informally compare Model.1 with model.2

```{r}
anova(model.1,model.2)
```

Finally, we can conclude that the model with the grip and arm is better. We can see that the residual some of squares went down by 25 points. 