---
title: "linear model from Web"
author: "Madeleine Alseryani"
date: "Spring 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
newdata<-data_frame(ARM=88, GRIP=94)
```



#### Predict at target point


```{r}
predict(model.1,newdata,interval="prediction")
```


#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point() + geom_lm()
```


## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```


### Numerical results 

```{r}
cor(SIMS~GRIP,data= data)
```

### Inferential  (Build model.2)
  
  ```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

#### predict model.2 at target point

```{r}
predict(model.2,newdata,interval="prediction")
```

#### now add the model fit to our plot for model.2
  
```{r}
basicNG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
```{r}
basicNG + geom_point() + geom_lm()
```

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

#### predict model.3 at target point
  
```{r}
predict(model.3,newdata,interval="prediction")
```

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```

### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```

## Informally compare Model.1 with model.2

```{r}
anova(model.1,model.2)
```