---
title: "linear model from Web"
author: "Madeleine Alseryani"
date: "Spring 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

In this scatterplot we can see that as you move to the right, the SIMS increases. So the more to the right we go, the higher it increases. Therefore, this scatterplot has a positive correlation.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation value from this data and scatterplot is 0.6860073

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
We know that the smaller the value for the residual standard error, the better the model will be. And the smaller the adjusted R-squared value, the better the model will be as well. According to the inferential results, we can see that the adjusted R-squared value is 0.467 and the residual standard error is 1.226. 


```{r}
newdata<-data_frame(ARM=88, GRIP=94)
```



#### Predict at target point


```{r}
predict(model.1,newdata,interval="prediction")
```


#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point() + geom_lm()
```

This scatterplot shows the 
## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

This scatterplot shows the same kind of pattern that the first scatterplot shows. As you move towards the right, the SIMS increases. So it looks like its going uphill and right hence, it has a positive correlation. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data= data)
```

The correlation value from this scatterplot is 0.6398458

### Inferential  (Build model.2)
  
  ```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

Based on the inferential results, the residual standard error is 1.295 and the adjusted R-squared is 0.4053. The smaller the residual standard error is the better the model is and the smaller the adjusted R-squared value is the better the model will be. 

#### predict model.2 at target point

```{r}
predict(model.2,newdata,interval="prediction")
```

#### now add the model fit to our plot for model.2
  
```{r}
basicNG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
```{r}
basicNG + geom_point() + geom_lm()
```

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The residual standard error and the 

#### predict model.3 at target point
  
```{r}
predict(model.3,newdata,interval="prediction")
```

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```

### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```

## Informally compare Model.1 with model.2

```{r}
anova(model.1,model.2)
```